Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-06-09 graviton spectra/content/e16.tex
adressed orange comments, modules in conjecture 4.11

\subsection{The lowest pieces and 3d $\mc N=8$ BLG theory}\label{sec:BLG}
\parsec[] The first nontrivial case is the weight ${(-2)}$ piece. We have the following

@@

\parsec[]
We wish to flag an appearance of $\mc F^{(-1)}_{\R\times \C}$ in supersymmetric physics in three-dimensions. There is a highly supersymmetric Chern-Simons-matter theory discovered independently by Bagger-Lambert \cite{Bagger_2007}, \cite{Bagger:2007jr} and Gustavsson \cite{Gustavsson:2007vu}. The aptly named BLG theory has $\mc N=8$ superconformal symmetry, and admits a holomorphic-topological twist that was characterized by Garner in \cite{Garner2022vds}.

The sheaf of complexes $\mc F^{(-1)}_{\R\times \C}$ matches the field contents of the holmorphic-topological twist of the BLG theory, and as such, it can be equipped with an $L_\infty$ structure under which it is perturbatively equivalent to the twisted BLG theory. In work-in-progress with Garner and Williams, we show that the action of $\mc F^{(0)}_{\R\times \C}$ on $\mc F^{(-1)}_{\R\times \C}$ in fact preserves this $L_\infty$-structure.

\brian{it's an abelian L-infinity structure right? So we can just say complexes.}

\surya{i thought the BLG theory has a quartic superpotential.}

\brian{The thing we don't mention so much is the BV structure.}

\brian{I think we can at least comment that the BV structure comes from the BR.}

@@

\item The final nontrivial bracket is more complicated. 
Given elements $B \otimes f \del_z^{1/2}, B'\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have
\begin{align*}
[B\otimes f \d z^{-1/2} , B' \otimes g \d z^{-1/2} ] & = \tr (B \star B') \otimes fg \del_z \\ & + \frac12 (B \star B')_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
& \in \Gamma (\hat D, T) \ltimes \left (\mf {sl}(4) \otimes \Gamma (\hat D, \mc O) \right ) .
\end{align*}
where again $\star$ denotes the Hodge star and the subscript of zero denotes projection to the traceless part. 
\brian{simplify last line so it is obviously a vector field}

\brian{Choose $\d z^{-1/2}$ or $\del_z^{1/2}$}
\end{itemize}

@@

\subsection{General summands and $E(1|6)$-modules}
We now move on to giving an explicit description of the general summand $\mc F^{(j)}$ for $j \geq 1$.

@@

\brian{Might be useful to point out that a systematic characterization of irreps of $E(1|6)$ is incomplete.}

\brian{But, we expect the modules appearing above to be irreducible.}

@@

In \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_4}$ is expressed as a sum of characters of irreducible representations of the 3d $\mc N = 8$ superconformal algebra that the authors call \textit{graviton representations}. Comparison with the above expansion suggests the following conjecture

>>>>

\subsection{The lowest pieces and minimally twisted rank 1 ABJM}\label{sec:BLG}
\parsec[] The first nontrivial case is the weight ${(-2)}$ piece. We have the following

@@

\parsec[]
We wish to flag an appearance of $\mc F^{(-1)}_{\R\times \C}$ in supersymmetric physics in three-dimensions. There is a highly supersymmetric Chern-Simons-matter theory discovered by \cite{} which describes the low-energy dynamics of a single M2 brane probing the origin in $\C^4$. The aptly named ABJM theory has a manifest $\mc N=6$ superconformal symmetry, and admits a holomorphic-topological twist that was characterized by Garner in \cite{Garner2022vds}. Non-perturbatively, it has an $\mc N=8$ superconformal symmetry, the enhancement to which is furnished by monopole operators.

The sheaf of complexes $\mc F^{(-1)}_{\R\times \C}$ matches the field contents of the holmorphic-topological twist of the rank 1 ABJM theory at level 1. In work-in-progress with Garner and Williams, we explicate the action of $\mc F^{(0)}_{\R\times \C}$ on $\mc F^{(-1)}_{\R\times \C}$ at the level of local operators in terms of currents. As we describe in the next subsection, the infinity jets at the origin of $\mc F^{(0)}_{\R\times \C}$ contain a copy of the minimally twisted three-dimensional $\mc N=8$ superconformal algebra. In keeping with the fact that the rank 1 level 1 ABJM theory only admits three-dimensional $\mc N=8$ superconformal symmetry after taking into account monopoles, we see that the currents realizing the $\mc F^{(0)}_{\R\times \C}$ action involves monopoles. The fact that the action is manifest from the perspective of this paper articulates a sense in which perturbative gravity may contain information about non-perturbative brane dynamics.

@@

\item The final nontrivial bracket is more complicated. 
Given elements $B \otimes f \del_z^{1/2}, B'\otimes g \del_z^{1/2} \in \Gamma( \hat D, \wedge^2 (\C^4) \otimes K^{1/2}_\C)$, we have
\begin{align*}
[B\otimes f \d z^{-1/2} , B' \otimes g \d z^{-1/2} ] & = \tr (B \star B') \otimes fg \del_z \\ & + \frac12 (B \star B')_0 \otimes \left (\del (f \d z^{-1/2} ) g \d z^{-1/2} + f \d z^{-1/2} \del (g \d z^{-1/2} ) \right ) \\
& \in \Gamma (\hat D, T) \ltimes \left (\mf {sl}(4) \otimes \Gamma (\hat D, \mc O) \right ) .
\end{align*}
where again $\star$ denotes the Hodge star and the subscript of zero denotes projection to the traceless part. 
\brian{simplify last line so it is obviously a vector field}
\surya{isnt the last line an $\mf{sl}_4$ current ?}
\brian{Choose $\d z^{-1/2}$ or $\del_z^{1/2}$}
\end{itemize}

@@

\subsection{General summands and $E(1|6)$-modules}
We now move on to giving an explicit description of the general summand $\mc F^{(j)}_{\R\times \C}$ for $j \geq 1$. By proposition \ref{prrop:ads4decomp} the costalks $\mc F^{(j)}_{\R\times \C, c} (0)$ are $E(1|6)$-modules. A full classification of irreducible $E(1|6)$-modules is incomplete. Nevertheless, we expect the modules we find are irreducible.

\surya{i think this is probably pretty quick just using $\mf{sl}_4$-rep theory}

@@

@@

In \cite[Eq. (2.15, 2.16)]{Bhattacharya:2008zy}, the index counting gravitons on $f_{AdS_4}$ is expressed as a sum of characters of irreducible representations of the 3d $\mc N = 8$ superconformal algebra that the authors call \textit{graviton representations}. In \cite[Table 9]{cordova2016multiplets} these representations are examples of short representations labeled $B_1(0)_{\Delta}^{(R_1,\cdots, R_4)}$. Here the superscripts and subscript denote the $\mf{so}(8)_R$ weights and scaling dimensions of a superconformal primary respectively.

\surya{we should pin down what values of $\Delta, R_i$ appear for us}

Comparison with the above expansion suggests the following conjecture

### 2023-06-09 graviton spectra/content/e36.tex
adressed orange comments, modules in conjecture 4.11

The decomposition of the local $L_\infty$-algebra $\Omega^{0,\bullet}_{\C^3}(\mc L^{r=0}_{AdS_7} )$ afforded by proposition \ref{prop:ads7decomp} induces a weight grading of $\widehat{E(5|10)}$ which extends the one on $E(5|10)$ that we have just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\begin{equation}\label{eqn:decomp2}
\widehat{E(5|10)} = \prod_{j \geq -1} U_j            
\end{equation}                      
were $U_{-1}$ is a $\C$-extension of $\tilde U_{-1}$ defined in the decomposition \eqref{eqn:decomp1} and for $j \geq 0$ the $U_j$'s are the same as in the non centrally extended case. As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible \surya{is this last sentence actually true? these aren't the same modules}

>>>>

The decomposition of the local $L_\infty$-algebra $\Omega^{0,\bullet}_{\C^3}(\mc L^{r=0}_{AdS_7} )$ afforded by proposition \ref{prop:ads7decomp} induces a weight grading of $\widehat{E(5|10)}$ which extends the one on $E(5|10)$ that we have just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\begin{equation}\label{eqn:decomp2}
\widehat{E(5|10)} = \prod_{j \geq -1} U_j            
\end{equation}                      
were $U_{-1}$ is a $\C$-extension of $\tilde U_{-1}$ defined in the decomposition \eqref{eqn:decomp1} and for $j \geq 0$ the $U_j$'s are the same as in the non centrally extended case. As a corollary, we see that each of the $E(3|6)$ modules which we have identified as the costalk at 0 $\mc G^{(j)}_{\C^3, c} (0)$ is in fact irreducible \surya{is this actually a corollary? these aren't the same modules}
